---
title: "Enos 2014 Replication"
author: "Helen Simpson"
date: "2/27/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
library(ri)
library(RItools)
library(car)
library(xtable)
library(effects)
library(RColorBrewer)
library(SparseM)
library(gt)
library(tidyverse)

options(scipen = 999)  ##set for non-scientific notaion output

##Load data
dat.all = read.csv('dataverse_files/pnas_data.csv')

#I'm sorry about the bad formatting, I don't have time this week to figure out how to make all this
#stuff look good.
```

Enos (2014) tests whether casual exposure to another demographic group causes a negative reaction to that group. Commuters who are randomly assigned to a train car with Spanish speaking collaborators will be less tolerant of Hispanics in their survey answers after 3 days. After 10 days, however, the effect will lessen. I replicate Enos's main results and tests the balance between the treatment and control groups using propensity scores.

#Table 1
```{r echo=FALSE}
##main_results.r
####primary randomization inferece
#this makes table 1

###inference
repeats = c("numberim","Remain","Englishlan")

x.names = paste(repeats,".x",sep="")
y.names = paste(repeats,".y",sep="")

covariates = c('line.x')

#splitting data into wait in car/ wait on platform
###treated first
final.mat = matrix(nrow = 0, ncol = 8)

subsets = c('all','no.car')

#cat('beginning inference \n')


for(subset in subsets){

	out.mat = matrix(nrow = length(repeats), ncol = 8)
	
	if(subset == 'all'){
		dat.subset = dat.all
		}
	if(subset ==  'no.car'){
		dat.subset = dat.all[dat.all$habits != 1,]
		}

		
	z.variable = 'treatment'
	
	for(j in 1:length(repeats)){
		dat.subset$x.new = (as.numeric(dat.subset[,x.names[j]])-1)/4  ##rescale x to 0-1
		dat.subset$y.new = (as.numeric(dat.subset[,y.names[j]])-1)/4  ##rescale y to 0-1
		dat.subset$Y = dat.subset$y.new - dat.subset$x.new
		
		dat.use = dat.subset[is.na(dat.subset$Y) == F,]
		
		#calcuate values for table 1
		x.sd = sd(dat.use$x.new,na.rm = T)
		x.mean = mean(dat.use$x.new,na.rm = T)
		y.mean = mean(dat.use$y.new,na.rm = T)
		y.treat = mean(dat.use$y.new[dat.use$treatment==1],na.rm = T)
	
		station.treatment.table = table(dat.use$station,dat.use[,z.variable])
		no.control.stations = names(which(station.treatment.table[,1] == 0))
		no.treatment.stations = names(which(station.treatment.table[,2] == 0))
		dat.use = dat.use[!dat.use$station%in%c(no.control.stations,no.treatment.stations),]
				
		
		dat.use$station = factor(dat.use$station)
		dat.use$treated_unit = factor(dat.use$treated_unit)
		Xs = data.matrix(dat.use[,covariates])
		
		perms <- genperms(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)
		probs = genprobexact(Z = dat.use[,z.variable], blockvar=dat.use$station, clustvar=dat.use$treated_unit)

		ate = estate(Y = dat.use$Y, Z = dat.use[,z.variable], X = Xs, prob = probs)
		Ys = genouts(Y = dat.use$Y, Z = dat.use[,z.variable], ate = 0)
		distout <- gendist(Ys,perms, prob=probs)
		disp =	dispdist(distout, ate = ate, display.plot = F)
	
		out.mat[j,1] = repeats[j]
		out.mat[j,2] = subset
		out.mat[j,3] = nrow(dat.use)
		out.mat[j,4] = ate
		out.mat[j,5] = disp$greater.p.value
		out.mat[j,6] = disp$lesser.p.value
		out.mat[j,7] = x.sd
		out.mat[j,8] = x.mean
		}
	final.mat = rbind(final.mat,out.mat)
	}

final.mat = as.data.frame(final.mat)
colnames(final.mat) = c('variable','subset','N','ate','greater.p.value','lesser.p.value','x.sd','x.mean')

final.mat.main = final.mat ##final.mat for output creation later

gt(final.mat.main)

```
#Table 2
```{r echo=FALSE}
##balance_check.r
###check to see if randomization created balanced samples in Enos experiment
####RdE September 2012
#first output is table 2

#test for balance of demographic characteristics between treatment and control groups
#code from Hannah Hardenbergh
out.balance.test = xBalance(fmla = treatment ~ liberal+republican+obama.disapprove+ride.everyday+voted.2010+romney.voter+Hispanics.x+age+residency.new+hispanic.new+college+income.new+male+white, data = dat.all, report = c("std.diffs","z.scores","adj.means","chisquare.test"), strata = factor(dat.all$station))

xtable.out.balance.text = xtable(out.balance.test)
print(xtable.out.balance.text, file = 'balance_table.tex',
	floating = FALSE)
xtable.out.balance.text %>% 
  select(`treatment=0`,
         `treatment=1`, 
         std.diff,
         z) %>% 
  gt(rownames_to_stub = TRUE)

```
#Extension
Enos argues that the treatment and control groups are very similar on a variety of demographic indicators. The balance test he performs in order to test this, however, is univariate. Propensity scores, described in section 10.3 of the textbook, allow us to test balance on all of the dimensions Enos uses simultaneously. The density plots below show propensity scores. They demonstrate that there is a substantial, but not perfect, overlap between the control and treatment groups. This confirms Enos's results from Table 2.
```{r echo=FALSE}
#Thanks to Mark for the idea and help with the code
obj <- glm(treatment ~ liberal + conservative + obama.disapprove + ride.everyday + voted.2010 + romney.voter + Hispanics.x + age + residency.new + hispanic.new + college + income.new + male + white, data = dat.all, family = "binomial")
predict.obj <- predict(obj, type = "response")
dat.all$treated.prob <- predict.obj

treatment.subset <- subset(dat.all, treatment == 1)
control.subset <- subset(dat.all, treatment == 0)

ggplot(control.subset, aes(x = treated.prob)) + geom_density(kernel = "gaussian") + labs(x = "Probability of Treatment", y = "Density", title = "Control Subjects") + theme_classic()
ggplot(treatment.subset, aes(x = treated.prob)) + geom_density(kernel = "gaussian") + labs(x = "Probability of Treatment", y = "Density", title = "Treatement Subjects") +theme_classic()

#if I had more time I would put these on the same plot and use different colors, or at least make the scales the same
```

#Bibliography

Enos, Ryan. (2014). "Causal effect of intergroup contact on exclusionary attitudes." *Proceedings of the National Academy of Sciences*, 111(10): 3669-3704.